Market Expectations and Mangerial Turnover

### 2024-03-03 paper.qmd
update

## Manager spell profiles

@@

data_helper <- spells |>
  mutate(row_id=row_number()) |>
  filter(is.na(Finish)&contract_expiry!="-") |>
  select(contract_expiry, Finish,row_id)
data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
spells |>
  mutate(row_id=row_number()) |>
  left_join(data_helper |> select(-Finish), by="row_id") |>
  mutate(Start = as.Date(Start),
         Finish = as.Date(Finish)) |>
  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
spells |> distinct(name,club,Finish) |> nrow()
# find duplicates for name,club,Finish
spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
# remove duplicates
spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) -> spells
spell <- spells |> select(club,Start,Finish) |> arrange(Finish)
spell |> filter(Finish-Start>0) -> spell
```

@@

- `name`: The name of the person in charge
- `club`: The club the manager was in charge of
- `position`: The position of the person in charge
- `Start`: The start date of the spell
- `Finish`: The end date of the spell
- `days_in_charge`: The number of days the manager was in charge of the club
- `season_start`: The start of the season the spell ended

>>>>

## Manager spell

@@

data_helper <- spells |>
  mutate(row_id=row_number()) |>
  filter(is.na(Finish)&contract_expiry!="-") |>
  select(contract_expiry, Finish,row_id)
data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
spells |>
  mutate(row_id=row_number()) |>
  left_join(data_helper |> select(-Finish), by="row_id") |>
  mutate(Start = as.Date(Start),
         Finish = as.Date(Finish)) |>
  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
spells |> distinct(name,club,Finish) |> nrow()
# find duplicates for name,club,Finish
#spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
# remove duplicates
spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) |> filter(Finish-Start>0) -> spells

@@

-   `name`: The name of of staff member
-   `club`: The club of the staff member
-   `position`: The position of the staff member
-   `appointed`: The start date of the spell
-   `contract_expiry`: The end date of the spell
-   `days_in_charge`: The number of days the manager was in charge of the club
-   `wins`: Number of wins for spell
-   `draws`: Number of draws for spell
-   `losses`: Number of losses for spell
-   `players_used`: Number of players used in the spell
-   `avg_goals_for`: Average goals scored per game
-   `avg_goals_against`: Average goals conceded per game
-    `ppm`: Points per match

```{r}
#|label: fig-managertype
#|fig-cap: "Word cloud of manager types"

# Use the wordcloud package to create a word cloud of manager types using position column
library(wordcloud)
library(tm)
library(SnowballC)
terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
  "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
  "1.FC Köln U17","1.FC Köln Yth.",
  "1.FC Köln U16"," II","1.FC Köln","Bor. M'gladbach",
  "Hertha BSC","F. Düsseldorf",
  "Velez Mostar","SSV Reutlingen","FV Ravensburg",
  "Fenerbahce","FC Teningen","FV Nimburg","Heart of Midl.",
  "Vetra","Sp.Genzano (PZ)","Honvéd FC","Olympiacos","Honvéd SE","Hungary",
  "ADO Den Haag(A)","Dordrecht'90","Haarlem","AZ Alkmaar","Roda JC","AZ '67",
  "Sparta R.","De Treffers","NEC Nijmegen","FC Oss","VV Gemert","PSV U21")
paste0("(",paste(terms_to_remove,collapse="|"),")")  -> remove_terms
spells |>
  str_remove(position,terms_to_remove[1]) %>%
  {table(.$position)}

spells |> mutate(
    staff_position = trimws(tolower(position)),
    staff_position = ifelse(staff_position=="manager","manager",staff_position),
    staff_position = ifelse(staff_position=="assistant manager","assistant manager",staff_position),
    staff_position = ifelse(staff_position=="caretaker manager","caretaker manager",staff_position),
    staff_position = ifelse(str_detect(staff_position,"player-coach"),"player-coach",staff_position),
    staff_position = ifelse(str_detect(staff_position,"director of football"),"director of football",staff_position),
    staff_position = ifelse(str_detect(staff_position,"technical director"),"technical director",staff_position),
    staff_position = ifelse(str_detect(staff_position,"director of professional football"),"director of professional football",staff_position),
    staff_position = ifelse(str_detect(staff_position,"sporting director"),"sporting director",staff_position),
    staff_position = ifelse(str_detect(staff_position,"academy manager"),"academy manager",staff_position),
    staff_position = ifelse(str_detect(staff_position,"advisor"),"advisor",staff_position),
    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position),
    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position)) -> spells

table(spells$staff_position[!is.na(spells$staff_position)]) |> sort(decreasing = TRUE)
```

```{r}

VCorpus <- Corpus(VectorSource(spells$position[!is.na(spells$position)]))
terms_to_remove <-c('Al-Ahli (UAE)','')
# Copy text to clipboard on Linux
text <- unique(spells$position[!is.na(spells$position)])
write(text, "| xclip -selection clipboard")

table(spells$position[!is.na(spells$position)])
VCorpus <- VCorpus |>
  tm_map(content_transformer(tolower)) |> 
  tm_map(removePunctuation) |> 
  tm_map(removeNumbers) |> 
  tm_map(removeWords, stopwords("en")) |> 
  tm_map(stripWhitespace) |> 
  TermDocumentMatrix() |> 
  as.matrix() |> 
  colSums() |> 
  sort(decreasing = TRUE) 
wordcloud(words = names(VCorpus), freq = VCorpus, min.freq = 1, scale = c(3, 0.5), colors = brewer.pal(8, "Dark2"))
```
